Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs

### 2020-02-04 main.tex
Proof of Theorem 4

% Custom packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{blkarray}
\usepackage{mathtools}
\usepackage{multirow}
\input{mathdef.tex}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

@@

The dynamics of the real system are described in continuous time. However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t$. For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$. We use bold symbols to denote sequences $\bz = (z_1,z_2,\dots)$.

@@

At the time step $n=N$, considering the confidence region $\cC_{[N],\delta}$ obtained in the model estimation phase, we formulate our robust control objective:
\begin{equation}
\label{eq:robust-control}
\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
\end{equation}
where $\bu = (u_{N+1},u_{N+2},\dots)$ and $\bw = (\omega_N, \omega_{N+1},\dots)$ are the sequences of future controls and perturbations, respectively. The rest of the paper will tackle the optimisation of this objective.

@@

The robust objective we consider becomes 
\begin{equation}
\label{eq:robust-control-disc}
\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bw))\right]}_{V^r(\ba)}
\end{equation}
where $x_n(\ba, \bw)$ is obtained by integrating \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.

@@

Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate. However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight.

However, under an additional smoothness assumption on $R$, we can bound this gap:
\begin{theorem}[Approximation gap]
\label{thm:control-error}
If the reward function $R$ is lipschitz, then we can bound the approximation error of \autoref{alg:full}:
\begin{equation*}
\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \cO\left(\frac{1}{\sqrt{N}}\right)
\end{equation*}
\end{theorem}

@@

\begin{table}[htbp]
	\caption{Mean and worst-case performance}
	\label{tab:results}
	\centering
	\begin{tabular}{lcccccc}
		\toprule
		\multicolumn{1}{l}{Task} &
		\multicolumn{3}{c}{Obstacle}    &
		\multicolumn{3}{c}{Driving}\\
		\cmidrule(lr){2-4}
		\cmidrule(lr){5-7}
		Perf. &
		\multicolumn{1}{c}{min} &
		\multicolumn{1}{c}{mean} &
		\multicolumn{1}{c}{failures} &
		\multicolumn{1}{c}{min} &
		\multicolumn{1}{c}{mean} & 
		\multicolumn{1}{c}{failures}\\
		\midrule
		Oracle & {11.6} & {14.2} & 0\% & {0} & {0} & 0\\
		{Nominal} & {2.8} & \textbf{13.8} & 4\% & {0} & {0} & 0 \\
		Robust & \textbf{10.4} & {13.0} & \textbf{0\%} & {0} & {0} & 0 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

@@

\begin{proof}
	The predictor designed in \autoref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}. Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.

	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bw}, \overline{\bw}]$, we also have for any sequence of controls $\bu$:
	\begin{align*}
	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bw} \leq \bw \leq \overline{\bw}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
	    &= \hat{V}^r(\bu)
	\end{align*}
\end{proof}

@@

We first bound the model estimation error.
\begin{lemma}
Under sufficient excitations in the features 
\begin{align}
\label{eq:excitation}
\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,i,j\in[p],\nonumber\\ \underline{\phi}^2 \leq \sum_k \sum_l \phi_{n,k,i}\Sigma_{p,k,l}^{-1}\phi_{n,l,j} \leq \overline{\phi}^2,
\end{align}
then,
\[\|A(\theta) - A(\theta_{[N],\lambda})\|_2 = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
\end{lemma}
\begin{proof}
By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $G_{[N],\lambda,i,j} \geq N\underline{\phi}^2 $

@@

And $A(\theta)$ belongs to a linear image of this ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
\begin{align*}
((A(\theta)&-A(\theta_{[N],\lambda}))^\transp (A(\theta) - A(\theta_{[N],\lambda})))_{i,j}\\
%&= (\phi_i(\theta-\theta_{[N],\lambda}))^\transp \phi_j(\theta-\theta_{[N],\lambda}) \\
&= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2} = \cO\left( \sqrt{\frac{\log N}{N}} \right) 
\end{align*}

@@

\begin{lemma}

\[\|\ox(t) - \ux(t)\| \leq C_\omega(t) +\cO\left( \sqrt{\frac{\log N}{N}} \right) \]
where $C_\omega(t)$ is the interval size $\|\ox(t) - \ux(t)\|$ obtained by running \eqref{eq:interval-predictor} with $\Delta A=0$.

\end{lemma}
\begin{proof}
Let $e = \ox - \ux$. Assuming that eventually after $n\geq N \geq N_0$, $A_0 = A(\theta_{[N],\lambda})$ becomes close enough to $A(\theta)$ to always be Metlzer. Then, \eqref{eq:interval-predictor} gives the dynamics:
\begin{align*}
\dot{e} = A_0e + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
\end{align*}
where $|M| = M^+ + M^-$.

Moreover, it holds that $-\ux^+ -\ox^- \leq e \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |e|$.

We define $V = e^\transp P e$, which is non-negative definite provided that
$
P>0,
$ and compute its derivative:
\begin{align*}
\dot{V} ={}& X^\transp
\begin{bmatrix}
A_0^\transp P + P A_0^\transp + Q & P|\Delta A| & P|D|\\
|\Delta A|^\transp P & -\alpha I_n & 0\\
D^\transp|P| & 0 & -\rho I_p
\end{bmatrix}
X\\
& - e^\transp Q e + \alpha |\ux^+ + \ox^-|^2 + \rho |\overline{\omega} - \underline{\omega}|^2
\end{align*}
with $X=\begin{bmatrix}
e\\ \ux^+ + \ox^- \\ \overline{\omega} - \underline{\omega}
\end{bmatrix}$. Hence, 
\begin{align*}
\dot{V} \leq {}& X^\transp
\underbrace{\begin{bmatrix}
A_0^\transp P + P A_0^\transp + Q + 2\alpha^2 I_p & P|\Delta A| & P|D|\\
|\Delta A|^\transp P & -\alpha I_n & 0\\
D^\transp|P| & 0 & -\rho I_p
\end{bmatrix}}_{\Upsilon}
X\\
& - e^\transp Q e + \rho |\overline{\omega} - \underline{\omega}|^2
\end{align*}

Thus, if $\Upsilon < 0$, $Q>0$, $\rho > 0$, $V$ is bounded and can only increases from $V(e(t_N)) = 0$ to a $V(e)$ such that:
\[
e^\transp Q e = X^\transp \Upsilon X + \rho |\overline{\omega} - \underline{\omega}|^2
\]
\end{proof}

@@

 For any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bw} \leq \bw \leq \overline{\bw}$, we clearly have 
 \[V(\bu)^r \leq V(\bu) = \expectedvalue_{\bw}\sum_n \gamma^n R(x_n)\]

 Moreover, by the inclusion property \eqref{eq:inclusion-property}, we have that $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \leq \max_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x)$. Assuming $R$ is $L$-lipschitz,
 \begin{align}
     V(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|_2\\
     &\leq L\sum_{n>N} \gamma^n C_{\omega,n} + \cO\left(\sqrt{\log N / N}\right))
 \end{align}
\end{proof}

>>>>

% Custom packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{blkarray}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{bm}
\input{mathdef.tex}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

@@

The dynamics of the real system are described in continuous time. However, all the sensing and control performed on-board happen in discrete time, with time-step $\dd t$. For any variable $z$, we use the subscript notation to refer to these discrete times: $z_n = z(t_n)$ with $t_n = n\dd t$. We use bold symbols to denote temporal sequences $\bz = (z_n)_{n\in\Natural}$.

@@

At the time step $n=N$, considering the confidence region $\cC_{[N],\delta}$ obtained in the model estimation phase, we formulate our robust control objective:
\begin{equation}
\label{eq:robust-control}
\sup_{\bu\in{(\Real^q)}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\bu,\bom))\right]}_{V^r(\bu)}
\end{equation}
where $\bu = (u_{N+1},u_{N+2},\dots)$ and $\bom = (\omega_N, \omega_{N+1},\dots)$ are the sequences of future controls and perturbations, respectively. The rest of the paper will tackle the optimisation of this objective.

@@

The robust objective we consider becomes 
\begin{equation}
\label{eq:robust-control-disc}
\sup_{\ba\in{\cA}^\Natural} \underbrace{\inf_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bom\in[\underline{\bom},\overline{\bom}]^\Natural}} \left[\sum_{n=N+1}^\infty \gamma^n R(x_n(\ba,\bom))\right]}_{V^r(\ba)}
\end{equation}
where $x_n(\ba, \bom)$ is obtained by integrating \eqref{eq:dynamics} with $u_n = \pi_{a_n}(x_n)$.

@@

Hence, by using enough computational budget $K$ for planning we can get as close as we want to the optimal surrogate value $\hat{V}^r(\bu^*)$, at a polynomial rate. However, there exists a gap between $\hat{V}^r$ and the true robust objective $V^r$, which stems from three approximations: (i) the true reachable set was approximated by an enclosing interval in \eqref{eq:inclusion-property}; (ii) the time-invariance of the dynamics uncertainty $A(\theta)\in\cC_{[N],\delta}$ was handled by the interval predictor \eqref{eq:interval-predictor} as if it were a time-varying uncertainty $\forall t, A(\theta(t))\in\cC_{[N],\delta}$ ; and (iii) the lower-bound $\sum\min\leq \min\sum$ used to define the surrogate objective \eqref{eq:surrogate_objective} is not tight. However, this gap can be bounded with additional assumptions:
\begin{theorem}[Sample complexity]
\label{thm:control-error}
Under some assumptions specified in the proof, which amounts to
\begin{enumerate}
	\item the reward function $R$ is lipschitz;
	\item a persistent excitation assumption;
	\item a stability condition in the form of an LMI;
\end{enumerate}
 we can bound the approximation error of \autoref{alg:full}:
\begin{equation*}
\hat{V}^r(\bu) \leq {V}^r(\bu) \leq V(\bu) \leq \hat{V}^r(\bu) + \Delta_\omega + \cO\left({\log N / N}\right)
\end{equation*}
where $\Delta_\omega$ is a constant specified in the proof, which corresponds to an irreductible suboptimality suffered from being robust to the perturbations $\omega(t)$, with knowledge of $A(\theta)$. % $\max_a \sum_n \min_\omega$
\end{theorem}

@@

\begin{table}[htbp]
	\caption{Performances on the Obstacle task}
	\label{tab:obstacle}
	\centering
	\begin{tabular}{lccc}
		\toprule
		\multirow{2}{*}{Agent} &
		\multicolumn{2}{c}{Return} &
		\multirow{2}{*}{Failures} \\
		\cmidrule{2-3} & min &
		mean $\pm$ std & \\
		\midrule
		Oracle & {11.6} & {$14.2 \pm 1.3$} & 0\% \\
		\midrule
		{Nominal} & {2.8} & \textbf{$13.8 \pm 2.0$} & {4\%} \\
		Robust & \textbf{10.4} & {$13.0 \pm 1.5$} & \textbf{0\%} \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[htbp]
	\caption{Performances on the Driving task}
	\label{tab:driving}
	\centering
	\begin{tabular}{lccc}
		\toprule
		\multirow{2}{*}{Agent} &
		\multicolumn{2}{c}{Return} &
		\multirow{2}{*}{Failures} \\
		\cmidrule{2-3} & min &
		mean $\pm$ std & \\
		\midrule
		Oracle & {6.9} & {7.4} & 0\% \\
		\midrule
		{Nominal K} & {3.8} & \textbf{4.6} \\
		{Nominal U} & {3.0} & {4.3} \\
		Robust & {3.04} & {13.0} & \textbf{0\%} \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{proof}
	The predictor designed in \autoref{sec:prediction} verifies the inclusion property \eqref{eq:inclusion-property}. Thus, for sequence of controls $\bu$, any dynamics $A(\theta)\in C_{[N],\delta}$, and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, the corresponding state at time $t_n$ is bounded by $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \geq \min_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x) = \underline{R}_n(\bu)$.

	Thus, by taking the min over $C_{[N],\delta}$ and $[\underline{\bom}, \overline{\bom}]$, we also have for any sequence of controls $\bu$:
	\begin{align*}
	    V^r(\bu) &= \min_{\substack{A(\theta)\in C_{[N],\delta}\\ \underline{\bom} \leq \bom \leq \overline{\bom}}} \sum_{n=N+1}^\infty \gamma^n R(x_n)\\
	    &\geq \sum_{n=N+1}^\infty \gamma^n \underline{R}_n(\bu)\\
	    &= \hat{V}^r(\bu)
	\end{align*}
\end{proof}

@@

We first bound the model estimation error.
\begin{lemma}
Under sufficient excitations in the features 
\begin{align}
\label{eq:excitation}
\exists \underline{\phi},\overline{\phi}>0, n_0: \forall n\geq n_0,\nonumber\\ \underline{\phi}^2 \leq \lambda(\Phi_{n}^\transp\Sigma_{p}^{-1}\Phi_{n}) \leq \overline{\phi}^2,
\end{align}
then,
\[\|A(\theta) - A(\theta_{[N],\lambda})\|_2 = \cO\left( \sqrt{\frac{\log N}{N}} \right) \]
\end{lemma}
\begin{proof}
By \eqref{eq:g_n_lambda} and \eqref{eq:excitation}, we have $\lambda_{\min}(G_{[N],\lambda,i,j}) \geq N\underline{\phi}^2 $

@@

And $A(\theta)$ belongs to a linear image of this ball. By writing a the $j^{th}$ column of a matrix $M$ as $M_j$, and its coefficient $i,j$ as $M_{i,j}$,
\begin{align*}
((A(\theta)&-A(\theta_{[N],\lambda}))^\transp (A(\theta) - A(\theta_{[N],\lambda})))_{i,j}\\
%&= (\phi_i(\theta-\theta_{[N],\lambda}))^\transp \phi_j(\theta-\theta_{[N],\lambda}) \\
&= (\theta-\theta_{[N],\lambda})^\transp\phi_{i}^{\transp}\phi_j(\theta-\theta_{[N],\lambda}) \\
&\leq \lambda_{\max}(\phi_{i}^{\transp}\phi_j) \|\theta - \theta_{[N],\lambda}\|_{2}^2 = \cO\left( {\frac{\log N}{N}} \right) 
\end{align*}

@@

\begin{lemma}
If there exist $P>0,Q_0\in\Real^{p\times p}$, $\rho>0$ such that
\begin{align*}
\begin{bmatrix}
A_0^\transp P + P A_0^\transp + Q_0 & P|D| & P|\Delta A| \\
|D|^\transp P & -\rho I_r & 0\\
|\Delta A|^\transp P & 0 & -\lambda_{\max}(|\Delta A|) I_p
\end{bmatrix}< 0,
\end{align*}
then for all $t> t_N$,
\[\|\ox(t) - \ux(t)\| \leq \left(C_0 + \cO\left({\frac{\log N}{N}} \right)\right)C_\omega(t) \]
where $C_\omega(t) = \sup_{\tau\in[t_N,t]} \|\overline{\omega}(\tau) - \underline{\omega}(\tau)\|_2^2$ and $C_0 = \sqrt{{\rho\lambda_{\max}(P)}/({\lambda_{\min}(P)\lambda_{\min}(Q_0)})}$.
\end{lemma}
\begin{proof}
Let $e = \ox - \ux$. Assuming that eventually after $n\geq N \geq N_0$, $A_0 = A(\theta_{[N],\lambda})$ becomes close enough to $A(\theta)$ to always be Metlzer. Then, \eqref{eq:interval-predictor} gives the dynamics:
\begin{align*}
\dot{e} = A_0e + |\Delta A|(\ox^+ + \ux^-) + |D|(\overline{\omega} - \underline{\omega})
\end{align*}
where $|M| = M^+ + M^-$.

We define $V = e^\transp P e$, which is non-negative definite provided that
$
P>0,
$ and compute its derivative:
\begin{align*}
\dot{V} ={}& X^\transp
\begin{bmatrix}
A_0^\transp P + P A_0^\transp + Q & P|D| & P|\Delta A| \\
|D|^\transp P & -\rho I_r & 0\\
|\Delta A|^\transp P & 0 & -\alpha I_p
\end{bmatrix}
X\\
& - e^\transp Q e + \alpha |\ux^+ + \ox^-|^2 + \rho |\overline{\omega} - \underline{\omega}|^2
\end{align*}
with $X=\begin{bmatrix}
e & \overline{\omega} - \underline{\omega} &  \ux^+ + \ox^-
\end{bmatrix}^\transp$, for any $Q\in\Real^{p\times p}$, $\rho,\alpha\in\Real$ .

Moreover, it holds that $-\ux^+ -\ox^- \leq e \leq \ox^+ + \ux^-$, which implies $|\ux^+ + \ox^-| \leq 2 |e|$. Hence,
\begin{align*}
\dot{V} \leq {}& X^\transp
\underbrace{\begin{bmatrix}
A_0^\transp P + P A_0^\transp + Q + 4\alpha I_p & P|D| & P|\Delta A| \\
|D|^\transp P & -\rho I_r & 0\\
|\Delta A|^\transp P & 0 & -\alpha I_p
\end{bmatrix}}_{\Upsilon}
X\\
& - e^\transp Q e + \rho \|\overline{\omega} - \underline{\omega}\|_2^2
\end{align*}

Thus, if we had $\Upsilon < 0$, $Q>0$, $\rho > 0$, then we would have
\[
\dot{V} \leq -\mu V + \rho \|\overline{\omega} - \underline{\omega}\|_2^2
\]
with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)}$. Since $V(t_N) = 0$, this further implies that for all $t>t_N$, 
\begin{equation}
\label{eq:lyap-bound}
V(t) \leq \frac{\rho}{\mu} C_\omega(t)
\end{equation}

We now examine the condition $\Upsilon < 0$.
We resort to its Schur complement: $\Upsilon < 0$ if and only if $\alpha > 0$ and $R > S$, where $S= \alpha^{-1}\begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}^\transp \begin{bmatrix}|\Delta A|^\transp P & 0\end{bmatrix}$ and $R$ is the top-left block of $-\Upsilon$:
\[R = \begin{bmatrix}
-A_0^\transp P - P A_0^\transp - Q - 4\alpha I_p & -P|D|\\
-|D|^\transp P & \rho I_r\\
\end{bmatrix}\]

Let $Q_0 = Q-4\alpha I_p$.
Assume that $P$ is fixed, we have $\lambda_{\max}(S) \leq \alpha^{-1}\lambda_{\max}(P)^2\lambda_{\max}(|\Delta A|)^2$.
Thus, by taking $\alpha_N = \lambda_{\max}(|\Delta A|)^2 = \cO(\log N / N)$, $S = \begin{bmatrix}
S_0 & 0\\0 & 0
\end{bmatrix}$ becomes $\cO(1)$ with respect to $N$.
Thus, we can always find a $Q_0$ such that
\[R-S = \begin{bmatrix}
-A_0^\transp P - P A_0^\transp - Q_0 - S_0 & -P|D|\\
-|D|^\transp P & \rho I_r\\
\end{bmatrix} > 0 \]

We recover \eqref{eq:lyap-bound} with $\mu = \frac{\lambda_{\min}(Q)}{\lambda_{\max}(P)} = \frac{\lambda_{\min}(Q_0) - \alpha_N}{\lambda_{\max}(P)}$.
Finally, we obtain
\begin{align*}
\|e(t)\|_2^2 &\leq \lambda_{\min}(P)^{-1} V(t)\\
& \leq \frac{\rho\lambda_{\max}(P)/\lambda_{\min}(P)}{\lambda_{\min}(Q_0) - \alpha_N} C_\omega(t)\\
\end{align*}
Developing at the first order in $\alpha_N$ gives
\begin{align*}
\|e(t)\|_2 &\leq C_0\left(1 + \frac{\alpha_N}{2\lambda_{\min}(Q_0)} + \cO(\alpha_N^2)\right)C_\omega(t)\\
&\leq \left(C_0 + \cO(\log N/N)\right)C_\omega(t)
\end{align*}
\end{proof}

@@

 For any sequence of controls $\bu$, dynamics $A(\theta)\in C_{[N],\delta}$ and perturbations $\underline{\bom} \leq \bom \leq \overline{\bom}$, we clearly have 
 \[V(\bu)^r \leq V(\bu) = \expectedvalue_{\bom}\sum_n \gamma^n R(x_n)\]

 Moreover, by the inclusion property \eqref{eq:inclusion-property}, we have that $\underline{x}_n \leq x_n \leq \overline{x}_n$, which implies that $R(x_n) \leq \max_{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}  R(x)$. Assuming $R$ is $L$-lipschitz,
 \begin{align*}
     V(\bu) - \hat{V}^r(\bu) &\leq \sum_{n=N+1}^\infty \gamma^n \underset{{x\in[\underline{x}_n(\bu), \overline{x}_n(\bu)]}}{(\max - \min)} R(x)\\
     &\leq \sum_{n=N+1}^\infty \gamma^n L \left\|\underline{x}_n(\bu) - \overline{x}_n(\bu)\right\|_2\\
     &\leq L(C_0 + \cO\left({\log N / N}\right)) \sum_{n>N} \gamma^n C_{\omega}(t_n)\\
     &= \Delta_\omega + \cO\left({\log N / N}\right)
 \end{align*}
 with $\Delta_\omega = L C_0\sum_{n>N} \gamma^n C_{\omega}(t_n)$.
\end{proof}
